Python as a machine learning language: experiences from the scikit-learn project

### 2013-06-15 paper.tex
Add Brian.
This way that makes it 15.

\author{Lars~Buitinck~\inst{1,2} \and
        Gilles~Louppe~\inst{1,2} \and
        Mathieu~Blondel~\inst{1,2} \and
        Fabian~Pedregosa~\inst{2} \and
        Andreas~Mueller~\inst{2} \and
        Olivier~Grisel~\inst{2} \and
        Vlad~Niculae~\inst{2} \and
        Peter~Prettenhofer~\inst{2} \and
        Alexandre~Gramfort~\inst{2} \and
        Jacques~Grobler~\inst{2} \and
        Robert~Layton~\inst{2} \and
        Jake~Vanderplas~\inst{2} \and
        Arnaud~Joly~\inst{2} \and
        Gaël~Varoquaux~\inst{2}}

>>>>

\author{Lars~Buitinck~\inst{1,2} \and
        Gilles~Louppe~\inst{1,2} \and
        Mathieu~Blondel~\inst{1,2} \and
        Fabian~Pedregosa~\inst{2} \and
        Andreas~Mueller~\inst{2} \and
        Olivier~Grisel~\inst{2} \and
        Vlad~Niculae~\inst{2} \and
        Peter~Prettenhofer~\inst{2} \and
        Alexandre~Gramfort~\inst{2} \and
        Jacques~Grobler~\inst{2} \and
        Robert~Layton~\inst{2} \and
        Jake~Vanderplas~\inst{2} \and
        Arnaud~Joly~\inst{2} \and
        Brian Holt~\inst{2} \and
        Gaël~Varoquaux~\inst{2}}
